---
title: "Natural Enemies and their Types"
author: |
  | Deependra Dhakal
  | Agriculture and Forestry University
  | \textit{ddhakal.rookie@gmail.com}
  | \url{https://rookie.rbind.io}
output: 
  binb::monash:
    toc: true
    keep_tex: true
    slide_level: 2
    includes:
      in_header: beamer_header_template.tex
colortheme: monashwhite
outertheme: smoothtree
innertheme: rounded
innercolortheme: rose
outercolortheme: whale
linkcolor: red
urlcolor: lightgrayd
titlepage: 
titlefontsize: 18pt # breaks custom \lineskip
fontsize: 11pt
classoption: "aspectratio=169" # "compressed"
bibliography: [./../bibliographies.bib]
header-includes: 
  - \AtBeginSubsection{}
---

```{r setup, include=FALSE}
library(knitr)
require(tidyverse)
set.seed(453)
# invalidate cache when the package version changes
knitr::opts_chunk$set(tidy = FALSE, echo = FALSE, 
                  message = FALSE, warning = FALSE,
                  out.width = "45%", cache = TRUE, 
                  dev.args=list(bg=grey(0.9), pointsize=11))
options(knitr.table.format = "latex")
options(knitr.kable.NA = "", digits = 2)
options(kableExtra.latex.load_packages = FALSE)
# Beamer cheatsheet can be found at:
# http://www.cpt.univ-mrs.fr/~masson/latex/Beamer-appearance-cheat-sheet.pdf
# All beamer themes and colorthemes can be assessed at:
# https://hartwork.org/beamer-theme-matrix/

# A complete book on biolgy view this link
# https://github.com/philschatz/biology-book/blob/master/SUMMARY.md
```

# Natural Enemy: Classification

##

```{r natural-enemy-classification}
tribble(
  ~"Taxonomic group", ~"Enemy group", ~"Effect on plant", 
  "Virus", "Pathogen", "Disease infection",
  "Phytoplasma", "Pathogen", "Disease infection",
  "Fungus", "Pathogen", "Disease infection",
  "Higher plant", "Parasite", "Infestation",
  "Nematode", "Parasite", "Infestation",
  "Insect", "Parasite", "Infestation",
  "Insect", "Herbivores", "Infestation",
  "Snail and slug", "Herbivores", "Infestation",
  "Vertebrate", "Herbivores", "Biting damage"
) %>% 
  knitr::kable(booktabs = TRUE, caption = "Taxonomic group of organisms and nature of damage to crops", longtable = TRUE) %>% 
  kableExtra::kable_styling(latex_options = "striped", font_size = 8)
```

# Insects

## Biological control

- Natural enemies in field should be conserved with a provision of sheltering and pollen resourceful flowering plants around. 

**Insect predators**

- Insects of the family Coccinellidae feed on Aphids, scale insects and mealy bugs
  - 2 spotted lady-beetle: _Adalla bipunctata_
  - 7 spotted lady-beetle: _Coccinella septumpunctata_
  - 9 spotted lady-beetle: _Coccinella novenpunctata_
  - Vadalia beetle: _Rodolia cardinalis_

- Mantids prey on smaller insects
- Syrphid fly predate on maggots and aphids
- Cicindellidae (Cicindella sexgutata) predate on rice earhead bug
- Lebellulidae: Naids feed on mosquito larvae
- Insects of family Chrysopidae feed on Aphids, scales, mealybugs and mites
- Crabidae
- Lampyridae
- Reduvidae
- _Xanthopimpla predator_ (Ichuenumonidae) predate on pupae of _Chilo partellus_

**Insect parasites**

- _Trichogramma minutum_ (Trichogrammatidae) and _Apantales flavipes_ (Braconidae) lay eggs on larvae of _Chilo partellus_
- _Tricholyga sorbillans_, _T. bomycis_ (Tachinidae)

**Nematode**: _Neoaplectema carpocarpsae_ parasite of codling moth

**Protozoa**: _Nosema bombycis_, _Farinocystis tribolii_

**Fungi**

- Aspergillus
- Beauveria
- Metarhizium anisopliae
- Spicaria
- Entomophthora lecanii
- Entomophthora sphaerosperma
- Coccus viridis

**Bacterial**

- Bacillus thuringiensis is effective against, _Heliocoverpa armigera_, _Pieries brassicae_, _Hellula undalis_, _Plodia interpunctella_ and _Tribolium confusum_

**Virus**

- NPV (Borrelina virus) is effective against Alfalfa caterpilla, Cabbage loper ( _Trichoplusia ni_), Tobaccoo caterpillar/Beet armyworm ( _Spodoptera litura_, _Spodoptera exigua_), _Heliothis zea_, Diamond back moth ( _Plutella xylostella_).
- Granulosis virus (Bergoldia virus) is effective against Potato tuber moth ( _Gnoremoschema opercullela_), Codling moth

- _Rhizoctonia solanii_ and _Didymella exitalis_ putrates kills hyphal cells of Ophiobolus graminis (Fungal pathogen of wheat)


# Bacterial agents

##

# Fungal hyperparasite

##

# Bibliography

## References
