---
title: "Defence mechanisms against pathogens, parasites, insects"
author: |
  | Deependra Dhakal
  | Assistant Professor
  | Agriculture and Forestry University
  | \textit{ddhakal.rookie@gmail.com}
  | \url{https://rookie.rbind.io}
output: 
  binb::monash:
    toc: true
    keep_tex: true
    slide_level: 2
    includes:
      in_header: beamer_header_template.tex
colortheme: monashwhite
outertheme: smoothtree
innertheme: rounded
innercolortheme: rose
outercolortheme: whale
linkcolor: red
urlcolor: lightgrayd
titlepage: agrobacterium-transformation.png
titlefontsize: 18pt # breaks custom \lineskip
fontsize: 11pt
classoption: "aspectratio=169" # "compressed"
bibliography: [./../bibliographies.bib]
header-includes: 
  - \AtBeginSubsection{}
---

```{r setup, include=FALSE}
library(knitr)
require(tidyverse)
set.seed(453)
# invalidate cache when the package version changes
knitr::opts_chunk$set(tidy = FALSE, echo = FALSE, 
                  message = FALSE, warning = FALSE,
                  out.width = "45%", cache = TRUE, 
                  dev.args=list(bg=grey(0.9), pointsize=11))
options(knitr.table.format = "latex")
options(knitr.kable.NA = "", digits = 2)
options(kableExtra.latex.load_packages = FALSE)
# Beamer cheatsheet can be found at:
# http://www.cpt.univ-mrs.fr/~masson/latex/Beamer-appearance-cheat-sheet.pdf
# All beamer themes and colorthemes can be assessed at:
# https://hartwork.org/beamer-theme-matrix/

# A complete book on biolgy view this link
# https://github.com/philschatz/biology-book/blob/master/SUMMARY.md
```

```{r}
# pdftools::pdf_convert("/home/deependra/ddhakal/000readables/pathology/2009_Encyclopedia of Microbiology_3rd edition.pdf",
#                       pages = 8, format = "png",
#                       filenames = "agrobacterium-transformation.png",
#                       dpi = 250)
# Overview of agrobacterium tumefaciens infection process. Upon activation of the VirA/VirG two-component signal transduction system by signals released from wounded plant cells, a single-strand transferred DNA (T-DNA) is processed from the Ti plasmid and delivered as a nucleoprotein complex (T-complex) to plant nuclei. Expression of T-DNA genes in the plant result in the loss of cell growth control and tumor formation.
# refer to text for more
```

# Defense mechanisms against pathogens, parasites

## 

- Genetic information (determines the form and function) is encoded as DNA or (exceptionally) RNA.
  - Nucleus
  - Mitochondria
  - Plasmid (autonomously replicating)
  - Chloroplasts
- A gene (in general) is characterized by:
  - 100-500 codon triplets
  - Coding and and non-coding region
  - Protein or RNA as code product
- Genetic processes
  - Replication
  - Transcription
  - Translation
  - Regulatory elements -- promoters, enhancers, silencers or terminators

# Gene for gene hypothesis

# Defense mechanisms against insects

# Bibliography

## References
